\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-05-10 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
CHANGES IN VERSION 1.5.6 -------------------------  o new ionSource, analyser, detectorType, title accessor methods    for MIAPE, pSet and MSnSet classes <2012-05-06 Sun>  o updated quantify example to use data(itraqdata) instead of    reading dummyiTRAQ.mzXML <2012-05-09 Wed>  o initial mzTab write support <2012-05-10 Thu>  o mzTab read support <2012-05-10 Thu>  o updated demo and io vignettes with mzTab info <2012-05-10 Thu>
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@65826 bc3139a8-67e5-0310-9ffc-ced21a209358

See also section \ref{sec:io2} to import quantitative data stored in spreadsheets into \R 
for further processing using \Rpackage{MSnbase}.

@@

>>>>

See also section \ref{sec:io2} to import quantitative data stored in spreadsheets into \R 
for further processing using \Rpackage{MSnbase}. The \texttt{MSnbase-io} vignette 
gives a general overview of \Rpackage{MSnbase}'s input/ouput capabilites.

@@

\Rpackage{MSnbase} also supports the \texttt{mzTab} 
format\footnote{\url{http://code.google.com/p/mztab/}}, a light-weight, tab-delimited 
file format for proteomics data. \texttt{mzTab} files can be read into \R with 
\Rfunction{readMzTabData} to create and \Robject{MSnSet} instance. 
\Robject{MSnSet} objects can also be exported to \texttt{mzTab} with the 
\Rfunction{writeMzTabData} function.

See the \texttt{MSnbase-io} vignette for a general overview of 
\Rpackage{MSnbase}'s input/ouput capabilites.
